---
title: "Developing Data Products Week 4 Assignment"
author: "Robert Levine"
date: "12/29/2019"
output:
  slidy_presentation: default
  ioslides_presentation:
    smaller: yes
    widescreen: yes
subtitle: Use the spacebar or arrow keys to navigate slides
---

## Coursera Reproducible Pitch

- URL: *https://github.com/manastiwari/Developing-Data-Products-Week-4-Course-Project*
- First, create a Shiny application and deploy it on Rstudio's servers.Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.
- Details are in this link:

URL: *https://www.coursera.org/learn/data-products/peer/tMYrn/course-project-shiny-application-and-reproducible-pitch*

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

## Overview

The shiny app plots different variables from the mtcars dataset provided with R against miles per gallon (mpg).

```{r }
head(mtcars)
```

## UI Code

```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
library(shiny)
shinyUI(fluidPage(
  
  # Application title
  titlePanel("Cars Dataset - Miles per Gallon"),
  
  sidebarPanel(
    
    selectInput("variable", "Variable:", 
                c("Cylinders" = "cyl",
                  "Transmission" = "am",
                  "Gears" = "gear"))
  ),
  
  mainPanel(
    # Output: Formatted text for caption ----
    h3(textOutput("caption")),
    
    # Output: Plot of the requested variable against mpg ----
    plotOutput("mpgPlot")
  )
))
```

## Server Code

```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
library(shiny)
library(plotly)
mpgData <- mtcars
mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))
shinyServer(function(input, output) {
  
  formulaText <- reactive({
    paste("mpg vs ", input$variable)
  })
  
  output$caption <- renderText({
    formulaText()
  })
  output$mpgPlot <- renderPlot({
    ggplot(mpgData, aes_string(y=input$variable, x="mpg")) + geom_point()
  })
  
})
```